\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
spell check

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Routing and
Transportation Analyzer}. AORTA is a platform designed for testing autonomous
vehicle behaviors and intersection policies. Autonomous vehicles, termed agents,
use behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. Intersection policies deisgnate
when it is safe for an agent to cross an intersection.  AORTA's goal is to allow
for the definition of new agent behaviors and intersection policies to optimize
autonomous traffic. Additionally, by assigning human-like behaviors such as the
``car following model'' \cite{brackstone1999car} to agents, and
traffic-signal-like policies to intersections, AORTA could potentially simulate
human traffic.

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation
of the real world in a few minutes. AORTA is available open-source and is
easily extensible \footnote{Code available at
\texttt{http://code.google.com/p/road-rage}}, making it easier for users to
test out a number of agent behaviors and intersection policies in a short
timespan.

@@

The builder works incrementally while parsing OSM graphs into the map model,
with each pass feeding the next. The map model is then stored in an XML format.
\begin{enumerate}
  \item OSM encodes many paths besides driveable roads, so the builder first filters
        these out. Next, the builder marks OSM nodes common to multiple roads, since
        they implicitly indicate intersections. Overpasses do not share nodes
        with the roads they cross \cite{osmOverpass}.
  \item OSM \emph{ways} (sequences of nodes) include many
        intersections, so the builder next splits ways into undirected
        segments of roads between exactly two intersections.
  \item The builder multiplies undirected roads into directed lanes in each
        direction (unless the road is marked one-way). The builder guesses the
        number of lanes based on OSM's ``road type'' tag or an explicit number of
        lanes, when that data is available.
  \item The builder constructs turns between incoming and outgoing lanes at each
        intersection. The angle between the two lanes determines whether the turn is
        a left, right, straight, or U-turn. When several lanes all cross into fewer
        lanes, the builder forces merging at the rightmost lanes. 
  \item Because turns are heuristically placed, the graph is often disconnected.
        In order to ensure that an agent will be able to reach any point in the map,
        the builder removes all but the largest strongly connected component of the
        digraph. Disconnected lanes are spliced out of larger roads, leaving
        geometric gaps, but correctly ensuring connectivity.
\end{enumerate}

@@

To introduce new agents into the simulation in real-time, users can create
\emph{generators} programatically or using the UI. The generator produces the
desired amount of traffic by initializing agents from random locations inside a
\textit{start} polygon to random destinations within a \textit{goal} polygon.
Users can draw these polyons by mouse in the UI, allowing specific traffic
patterns like rush-hour scenarios to be easily simulated. A generator polygon
may also cover the entire map, uniformly distributing traffic everywhere.

@@

Intersections check for collisions by verifying no two agents are simultaenously
performing a conflicting turn. AORTA has a low-granularity model of turn
conflict. If two vehicles at any point along two different turns could ever come
into contact, then the turns are always in conflict, no matter where the agents
actually are along that turn. This is visualized in figure \ref{fig:conflicts}.
Further work is required before higher granularity can be introduced through
space-time tiling intersections \cite{JAIR08-dresner}, due to some of the
complex intersection geometries inferred from OSM. An example of such a complex
intersection is shown in figure \ref{fig:crazyIntersection}.

@@

To pick turns, agent behaviors consult a route strategy. Two simple
implementations exist already: a static route using A* \cite{astar} and a
drunken walk that probabilistically moves towards the destination. Users can
experiment with dynamic replanning or hierarchial planning
\cite{Botea04nearoptimal} without modifying any code other than creating a new
route implementation. Route policies could also interact with a single central
manager to gain some sort of global insight or with autonomous intersections to
avoid congestion.

@@

The speed of simulation depends on the step duration dt, the map size, and the
number of agents. A measure independent of these factors is the number of agent
steps per second. On a 2.4 GHz machine, this can be observed to average at
about 150,000, a number comparable to existing simulators \cite{SUMOthesis}.
When the time step is 0.1 seconds, this means 15,000 agents can be comfortably
simulated in real-time. Further optimizations are planned.

@@

The number of agents driving at some time changes because the continuous
generator introduces a new agent every second. This count reaches a steady state
when the generator introduces an agent at the same rate as older agents finish
their route. Figure \ref{fig:agent_cnt_atx} reveals that autonomous reservations
let agents reach their destination twice as quickly as the competition in
Austin, with a steady-state of about 400 agents. There, the count for traffic
signals continues to increase because gridlock occurred in one segment of the
map, causing agents to not finish their route. Figure
\ref{fig:agent_cnt_houston} revals a similar trend in Houston, except that
gridlock occurred both during the trial with traffic signals and stop signs.
Unexpected starvation was also observed: although the signals cycle through
turns regularly, agents cannot proceed when the previous cycle caused a
destination lane to fill and become blocked.

@@

The authors would like to thank Dr. Michael Quinlan for his support during the
seminal stages of AORTA and all OpenStreetMap contributers for collecting the
map data used in this work. Efforts by the Freshman Research Initiative,
College of Natural Sciences, UT Austin have allowed for the development of this
research.

>>>>

This paper introduces an open source multigent microscopic traffic simulator
called AORTA, which stands for \textit{Approximately Orchestrated Routing and
Transportation Analyzer}. AORTA is a platform designed for testing autonomous
vehicle behaviors and intersection policies. Autonomous vehicles, termed agents,
use behaviors to interact with one another, follow intersection policies, and
decide on both long term and short term actions. Intersection policies designate
when it is safe for an agent to cross an intersection.  AORTA's goal is to allow
for the definition of new agent behaviors and intersection policies to optimize
autonomous traffic. Additionally, by assigning human-like behaviors such as the
``car following model'' \cite{brackstone1999car} to agents, and
traffic-signal-like policies to intersections, AORTA could potentially simulate
human traffic.

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation
of the real world in a few minutes. AORTA is available open-source and is
easily extensible \footnote{Code available at
\texttt{http://code.google.com/p/road-rage}}, making it easier for users to
test out a number of agent behaviors and intersection policies in a short
time span.

@@

The builder works incrementally while parsing OSM graphs into the map model,
with each pass feeding the next. The map model is then stored in an XML format.
\begin{enumerate}
  \item OSM encodes many paths besides drivable roads, so the builder first filters
        these out. Next, the builder marks OSM nodes common to multiple roads, since
        they implicitly indicate intersections. Overpasses do not share nodes
        with the roads they cross \cite{osmOverpass}.
  \item OSM \emph{ways} (sequences of nodes) include many
        intersections, so the builder next splits ways into undirected
        segments of roads between exactly two intersections.
  \item The builder multiplies undirected roads into directed lanes in each
        direction (unless the road is marked one-way). The builder guesses the
        number of lanes based on OSM's ``road type'' tag or an explicit number of
        lanes, when that data is available.
  \item The builder constructs turns between incoming and outgoing lanes at each
        intersection. The angle between the two lanes determines whether the turn is
        a left, right, straight, or U-turn. When several lanes all cross into fewer
        lanes, the builder forces merging at the rightmost lanes. 
  \item Because turns are heuristically placed, the graph is often disconnected.
        In order to ensure that an agent will be able to reach any point in the map,
        the builder removes all but the largest strongly connected component of the
        digraph. Disconnected lanes are spliced out of larger roads, leaving
        geometric gaps, but correctly ensuring connectivity.
\end{enumerate}

@@

To introduce new agents into the simulation in real-time, users can create
\emph{generators} programatically or using the UI. The generator produces the
desired amount of traffic by initializing agents from random locations inside a
\textit{start} polygon to random destinations within a \textit{goal} polygon.
Users can draw these polygons by mouse in the UI, allowing specific traffic
patterns like rush-hour scenarios to be easily simulated. A generator polygon
may also cover the entire map, uniformly distributing traffic everywhere.

@@

Intersections check for collisions by verifying no two agents are simultaneously
performing a conflicting turn. AORTA has a low-granularity model of turn
conflict. If two vehicles at any point along two different turns could ever come
into contact, then the turns are always in conflict, no matter where the agents
actually are along that turn. This is visualized in figure \ref{fig:conflicts}.
Further work is required before higher granularity can be introduced through
space-time tiling intersections \cite{JAIR08-dresner}, due to some of the
complex intersection geometries inferred from OSM. An example of such a complex
intersection is shown in figure \ref{fig:crazyIntersection}.

@@

To pick turns, agent behaviors consult a route strategy. Two simple
implementations exist already: a static route using A* \cite{astar} and a
drunken walk that probabilistically moves towards the destination. Users can
experiment with dynamic replanning or hierarchical planning
\cite{Botea04nearoptimal} without modifying any code other than creating a new
route implementation. Route policies could also interact with a single central
manager to gain some sort of global insight or with autonomous intersections to
avoid congestion.

@@

The speed of simulation depends on the step duration $dt$, the map size, and the
number of agents. A measure independent of these factors is the number of agent
steps per second. On a 2.4 GHz machine, this can be observed to average at
about 150,000, a number comparable to existing simulators \cite{SUMOthesis}.
When the time step is 0.1 seconds, this means 15,000 agents can be comfortably
simulated in real-time. Further optimizations are planned.

@@

The number of agents driving at some time changes because the continuous
generator introduces a new agent every second. This count reaches a steady state
when the generator introduces an agent at the same rate as older agents finish
their route. Figure \ref{fig:agent_cnt_atx} reveals that autonomous reservations
let agents reach their destination twice as quickly as the competition in
Austin, with a steady-state of about 400 agents. There, the count for traffic
signals continues to increase because gridlock occurred in one segment of the
map, causing agents to not finish their route. Figure
\ref{fig:agent_cnt_houston} reveals a similar trend in Houston, except that
gridlock occurred both during the trial with traffic signals and stop signs.
Unexpected starvation was also observed: although the signals cycle through
turns regularly, agents cannot proceed when the previous cycle caused a
destination lane to fill and become blocked.

@@

The authors would like to thank Dr. Michael Quinlan for his support during the
seminal stages of AORTA and all OpenStreetMap contributors for collecting the
map data used in this work. Efforts by the Freshman Research Initiative,
College of Natural Sciences, UT Austin have allowed for the development of this
research.
